Quotients of the magmatic operad:\\ lattice structures and convergent rewrite systems

### 2018-09-07 Mag_quotients.tex
Passe partie 2

We denote by $\IMag$ the set of operadic ideals of $\KMag$ and we set
\begin{equation} \label{equ:definition_of_QMag}
    \QMag := \Big\{\KMag/_I :  I\in\IMag\Big\},
\end{equation}
as the set of the quotients of the linear magmatic operad. Given
$\KMag/_I \in \QMag$ and $x \in \KMag$, we denote by $[x]_I$ the
$I$-equivalence of $x$. Observe that $\KMag/_I$ is generated as an
operad by $[\Product]_I$. Moreover, given two  elements $\Oca_1$ and
$\Oca_2$ of $\QMag$, we denote by $\Hom\left(\Oca_1,\Oca_2\right)$ the
set of linear operad morphisms from $\Oca_1$ to~$\Oca_2$.
\medbreak

\begin{Proposition} \label{prop:endomorphisms_of_magmatic_operads}
    For any $\Oca_1, \Oca_2 \in \QMag$, the set
    $\Hom\left(\Oca_1,\Oca_2\right)$ admits a vector space structure.
    Moreover, its dimension is equal to $0$ or $1$ and every nonzero
    morphism is surjective.
\end{Proposition}
\begin{proof}
    Let $I_1, I_2 \in \IMag$ such that $\Oca_1 = \KMag/_{I_1}$ and
    $\Oca_2 = \KMag/_{I_2}$. Since $\Oca_1$ is generated by the binary
    element $[\Product]_{I_1}$, a morphism $\varphi:\Oca_1\to\Oca_2$ is
    uniquely determined by $\varphi\left([\Product]_{I_1}\right)$.
    Moreover, $\varphi\left([\Product]_{I_1}\right)$ has arity $2$ in
    $\Oca_2$. Hence, $\varphi\left([\Product]_{I_1}\right)$ belongs to
    the line spanned by the binary generator of $\Oca_2$, that is there
    exists a scalar $\lambda\in\K$ such that
    \begin{math}
        \varphi\left([\Product]_{I_1}\right)
        = \lambda[\Product]_{I_2}.
    \end{math}
    If there exists such a $\lambda$ different from zero, then for every
    nonzero scalar $\mu$, we have a well-defined operad morphism
    $\psi:\Oca_1\to\Oca_2$ satisfying
    \begin{math}
        \psi([\Product]_{I_1}) =\mu[\Product]_{I_2}
        = \left(\mu/\lambda\right)\varphi([\Product]_{I_1}).
    \end{math}
    Hence, $\Hom\left(\Oca_1,\Oca_2\right)$ is either reduced to the
    zero morphism or it is in one-to-one correspondence with $\K$, which
    proves that $\Hom\left(\Oca_1,\Oca_2\right)$ is a vector space of
    dimension at most $1$. Moreover, if $\varphi$ is different from $0$,
    that is there is a nonzero scalar such that
    $\varphi([\Product]_{I_1}) =\lambda[\Product]_{I_2}$, we have
    $\varphi(1/\lambda[\Product]_{I_1}) =[\Product]_{I_2}$, so that
    $\varphi$ is surjective.
\end{proof}
\medbreak

@@

\begin{Proposition} \label{prop:order_relations_on_QMag_and_ideals}
    Let $\Oca_1=\KMag/_{I_1}$ and $\Oca_2=\KMag/_{I_2}$ be two operads
    of $\QMag$. We have $\Oca_2\OrdQMag\Oca_1$ if and only if
    $I_1\subseteq I_2$.
\end{Proposition}
\begin{proof}
  Since, by Proposition~\ref{prop:endomorphisms_of_magmatic_operads},
  $\Hom\left(\Oca_1,\Oca_2\right)$ is a vector space of
  dimension at most~$1$, it contains a nonzero morphism if and only if
  the morphism $\bar{\varphi}:\Oca_1\to\Oca_2$ satisfying
  $\bar{\varphi}([\Product]_{I_1})=[\Product]_{I_2}$ is well-defined,
  which means that $\Oca_2\OrdQMag\Oca_1$ is equivalent to this
  condition. Moreover, by the universal property of the quotient,
  $\bar{\varphi}$ is well-defined if and only if $I_1$ is included
  in the kernel of the morphism $\varphi:\KMag\to\Oca_2$ defined by
  $\varphi(\Product)=[\Product]_{I_1}$. This kernel is equal to
  $I_2$, so that $\bar{\varphi}$ is well-defined if and only if
  $I_1$ is included in $I_2$, which concludes the proof.
\end{proof}
\medbreak

@@

Given two operads $\Oca_1=\KMag/_{I_1}$ and $\Oca_2=\KMag/_{I_2}$ of
$\QMag$, let us define
\begin{equation} \label{equ:inf_QMag}
    \Oca_1\InfQMag \Oca_2 := \KMag/_{I_1+I_2}
\end{equation}
and
\begin{equation} \label{equ:sup_QMag}
    \Oca_1\SupQMag \Oca_2 := \KMag/_{I_1\cap I_2}.
\end{equation}
Explicitly, for every positive integer $n$,
$\left(\Oca_1\InfQMag\Oca_2\right)(n)$ (resp.
$\left(\Oca_1\SupQMag\Oca_2\right)(n)$) is the quotient of vector spaces
$\KMag(n)/_{I_1(n)+I_2(n)}$ (resp.
$\KMag(n)/_{I_1(n)\cap I_2(n)}$).
\medbreak

\begin{Theorem} \label{thm:lattice_structure_of_QMag}
  The tuple $\LatQMag$ is a lattice.
\end{Theorem}
\begin{proof}
  First, we observe that the map $\Oca:\IMag\to\QMag$ defined by
  $\Oca(I) :=\KMag/_I$ is a bijection: it is surjective by definition of
  $\QMag$ and it is injective since $\Oca(I_1)=\Oca(I_2)$ implies that
  the kernel of the natural projection $\KMag\to\Oca(I_1)=\Oca(I_2)$ is
  both equal to $I_1$ and $I_2$. Moreover, from
  Proposition~\ref{prop:order_relations_on_QMag_and_ideals},
  $\Oca_2\OrdQMag\Oca_1$ is equivalent to $I_1\subseteq I_2$, so that
  $\OrdQMag$ is a partial order relation on $\QMag$ and $\Oca$ is a
  decreasing bijection. The tuple $\left(\IMag,\subseteq,\cap,+\right)$
  being a lattice, the decreasing bijection $\Oca$ induces lattice
  operations on $\QMag$, precisely $\InfQMag$ and $\SupQMag$ by
  definition.
\end{proof}
\medbreak

The union of generating sets of the two operadic ideals $I_1$ and $I_2$
is a generating set of $I_1+I_2$, so that the union of generating
relations for the two operads $\Oca_1$ and $\Oca_2$ of $\QMag$ forms a
generating set for the relations of $\Oca_1\InfQMag\Oca_2$. However, the
authors do not know how to compute a generating set of the intersection
of ideals (it is not the intersection of generating relations), so that
we do not know how to compute generating relations for
$\Oca_1\SupQMag\Oca_2$.
\medbreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hilbert series and Grassmann formula}
In order to show a Grassmann formula analog for $\LatQMag$, we need the
following lemma.
\medbreak

\begin{Lemma}
    \label{lem:lattice_structure_and_coefficients_of_Hiblert_series}
    Let $\Oca_1$ and $\Oca_2$ be two operads of $\QMag$. For every
    positive integer $n$, we have
    \begin{equation}
    \label{equ:lattice_structure_and_coefficients_of_the_Hiblert_series}
        \dim{\left(\left(\Oca_1\InfQMag\Oca_2\right)(n)\right)}+
        \dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)(n)\right)}=
        \dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}.
    \end{equation}
\end{Lemma}
\begin{proof}
    Let $I_1, I_2 \in \IMag$ such that $\Oca_1 = \KMag/_{I_1}$ and
    $\Oca_2 = \KMag/_{I_2}$. For every integer $n$, we have
    \begin{equation}\begin{split}
        &\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}+
            \dim{\left(\Oca_1\SupQMag\Oca_2(n)\right)}\\
        &=\dim{\Big(\KMag(n)/_{\left(I_1+I_2\right)(n)}\Big)}+
            \dim{\Big(\KMag(n)/_{\left(I_1\cap I_2\right)(n)}\Big)}\\
        &=\dim{\left(\KMag(n)\right)}-\dim{\left(I_1(n)+I_2(n)\right)}
            +\dim{\left(\KMag(n)\right)}
            -\dim{\left(I_1(n)\cap I_2(n)\right)} \\
        &=\dim{\left(\KMag(n)\right)}-\dim{\left(I_1(n)\right)}
            + \dim{\left(\KMag(n)\right)}-\dim{\left(I_2(n)\right)}\\
        &=\dim{\Big(\KMag(n)/_{I_1(n)}\Big)}
            +\dim{\Big(\KMag(n)/_{I_2(n)}\Big)}\\
        &=\dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}.
    \end{split}\end{equation}
    The third equality is due to the Grassmann formula applied to the
    subspaces $I_1(n)$ and $I_2(n)$ of $\KMag(n)$.
\end{proof}
\medbreak

@@

\begin{Theorem}
    \label{thm:Grassmann_formula_for_Hilbert_series_of_QMag}
    Let $\Oca_1$ and $\Oca_2$ be two operads of $\QMag$. We have
    \begin{equation} \label{equ:lattice_structure_and_Hiblert_series}
        \HilbertSeries_{\Oca_1\InfQMag\Oca_2}(t)
        +\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)
        =\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t).
    \end{equation}
\end{Theorem}
\begin{proof}
    We have
    \begin{equation}\begin{split}
        \HilbertSeries_{\Oca_1\InfQMag\Oca_2}(t)
        +\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)&
        =\sum_{n\in\N}\dim{\left(\left(\Oca_1\InfQMag\Oca_2\right)(n)
            \right)}t^n
            +\sum_{n\in\N}\dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)
            (n)\right)}t^n\\
        &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}
            +\dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)(n)
        \right)}\Big)t^n\\
        &=\sum_{n\in\N}\Big(\dim{\left(\Oca_1(n)\right)}
            +\dim{\left(\Oca_2(n)\right)}\Big)t^n\\
        &=\sum_{n\in\N}\dim{\left(\Oca_1(n)\right)}t^n+\sum_{n\in\N}
            \dim{\left(\Oca_2(n)\right)}t^n\\
        &=\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t),
    \end{split}\end{equation}
    where the third equality is due to
    Lemma~\ref{lem:lattice_structure_and_coefficients_of_Hiblert_series}.
\end{proof}
\medbreak

>>>>

We denote by $\IMag$ the set of operadic ideals of $\KMag$ and we set
\begin{equation} \label{equ:definition_of_QMag}
    \QMag := \Big\{\KMag/_I :  I\in\IMag\Big\},
\end{equation}
as the set of the quotients of the linear magmatic operad. Given
$\KMag/_I \in \QMag$ and $x \in \KMag$, we denote by $[x]_I$ the
$I$-equivalence class of $x$. Observe that $\KMag/_I$ is generated as an
operad by $[\Product]_I$ (where, recall, $\Product$ is the binary
generator of $\Mag$ and thus also of $\KMag$). Moreover, given two
elements $\Oca_1$ and $\Oca_2$ of $\QMag$, we denote by
$\Hom\left(\Oca_1,\Oca_2\right)$ the set of linear operad morphisms from
$\Oca_1$ to~$\Oca_2$.
\medbreak

\begin{Proposition} \label{prop:endomorphisms_of_magmatic_operads}
    For any $\Oca_1, \Oca_2 \in \QMag$, the set
    $\Hom\left(\Oca_1,\Oca_2\right)$ admits a vector space structure.
    Moreover, its dimension is equal to $0$ or $1$ and every nonzero
    morphism is surjective.
\end{Proposition}
\begin{proof}
    Let $I_1, I_2 \in \IMag$ such that $\Oca_1 = \KMag/_{I_1}$ and
    $\Oca_2 = \KMag/_{I_2}$. Since $\Oca_1$ is generated by the binary
    element $[\Product]_{I_1}$, a morphism $\varphi:\Oca_1\to\Oca_2$ is
    uniquely determined by $\varphi\left([\Product]_{I_1}\right)$.
    Moreover, $\varphi\left([\Product]_{I_1}\right)$ has arity $2$ in
    $\Oca_2$. Hence, $\varphi\left([\Product]_{I_1}\right)$ belongs to
    the line spanned by the binary generator of $\Oca_2$, that is there
    exists a scalar $\lambda\in\K$ such that
    \begin{math}
        \varphi\left([\Product]_{I_1}\right)
        = \lambda[\Product]_{I_2}.
    \end{math}
    If there exists such a $\lambda$ different from zero, then for every
    nonzero scalar $\mu$, we have a well-defined operad morphism
    $\psi:\Oca_1\to\Oca_2$ satisfying
    \begin{math}
        \psi([\Product]_{I_1}) =\mu[\Product]_{I_2}
        = \left(\mu \lambda^{-1}\right)\varphi([\Product]_{I_1}).
    \end{math}
    Hence, $\Hom\left(\Oca_1,\Oca_2\right)$ is either reduced to the
    zero morphism or it is in one-to-one correspondence with $\K$, which
    proves that $\Hom\left(\Oca_1,\Oca_2\right)$ is a vector space of
    dimension at most $1$. Moreover, if $\varphi$ is different from $0$,
    that is there is a nonzero scalar such that
    \begin{math}
        \varphi\left([\Product]_{I_1}\right) = \lambda[\Product]_{I_2},
    \end{math}
    we have
    \begin{math}
        \varphi\left(\lambda^{-1}[\Product]_{I_1}\right)
        = [\Product]_{I_2},
    \end{math}
    so that $\varphi$ is surjective.
\end{proof}
\medbreak

@@

\begin{Proposition} \label{prop:order_relations_on_QMag_and_ideals}
    Let $\Oca_1=\KMag/_{I_1}$ and $\Oca_2=\KMag/_{I_2}$ be two operads
    of $\QMag$. We have $\Oca_2\OrdQMag\Oca_1$ if and only if
    $I_1\subseteq I_2$.
\end{Proposition}
\begin{proof}
    Since, by Proposition~\ref{prop:endomorphisms_of_magmatic_operads},
    $\Hom\left(\Oca_1,\Oca_2\right)$ is a vector space of
    dimension at most~$1$, it contains a nonzero morphism if and only if
    the morphism $\bar{\varphi}:\Oca_1\to\Oca_2$ satisfying
    \begin{math}
        \bar{\varphi}\left([\Product]_{I_1}\right) = [\Product]_{I_2}
    \end{math}
    is well-defined, which means that $\Oca_2\OrdQMag\Oca_1$ is
    equivalent to this condition. Moreover, by the universal property
    of the quotient, $\bar{\varphi}$ is well-defined if and only if
    $I_1$ is included in the kernel of the morphism
    $\varphi:\KMag\to\Oca_2$ defined by
    \begin{math}
        \varphi(\Product) = [\Product]_{I_1}.
    \end{math}
    \Todo{S: plutôt $[\Product]_{I_2}$ ??}
    This kernel is equal to $I_2$, so that $\bar{\varphi}$ is
    well-defined if and only if $I_1$ is included in $I_2$, which
    concludes the proof.
\end{proof}
\medbreak

@@

Given two operads $\Oca_1=\KMag/_{I_1}$ and $\Oca_2=\KMag/_{I_2}$ of
$\QMag$, let us define
\begin{equation} \label{equ:inf_QMag}
    \Oca_1\InfQMag \Oca_2 := \KMag/_{I_1+I_2}
\end{equation}
and
\begin{equation} \label{equ:sup_QMag}
    \Oca_1\SupQMag \Oca_2 := \KMag/_{I_1\cap I_2}.
\end{equation}
Explicitly, for every positive integer $n$,
$\left(\Oca_1\InfQMag\Oca_2\right)(n)$ (resp.
$\left(\Oca_1\SupQMag\Oca_2\right)(n)$) is the quotient vector space
$\KMag(n)/_{I_1(n)+I_2(n)}$ (resp.
$\KMag(n)/_{I_1(n)\cap I_2(n)}$).
\medbreak

\begin{Theorem} \label{thm:lattice_structure_of_QMag}
    The tuple $\LatQMag$ is a lattice.
\end{Theorem}
\begin{proof}
    First, we observe that the map $\Oca:\IMag\to\QMag$ defined by
    $\Oca(I) := \KMag/_I$ is a bijection: it is surjective by definition
    of $\QMag$ and it is injective since
    \begin{math}
        \Oca\left(I_1\right) = \Oca\left(I_2\right)
    \end{math}
    implies that the kernel of the natural projection
    \begin{math}
        \KMag\to\Oca\left(I_1\right) = \Oca\left(I_2\right)
    \end{math}
    is equal to both $I_1$ and $I_2$. Moreover, from
    Proposition~\ref{prop:order_relations_on_QMag_and_ideals},
    $\Oca_2\OrdQMag\Oca_1$ is equivalent to $I_1\subseteq I_2$, so that
    $\OrdQMag$ is a partial order relation on $\QMag$ and $\Oca$ is a
    decreasing bijection. The tuple
    $\left(\IMag,\subseteq,\cap,+\right)$ being a lattice, the
    decreasing bijection $\Oca$ induces lattice operations on $\QMag$,
    precisely $\InfQMag$ and $\SupQMag$ by definition.
\end{proof}
\medbreak

The union of the generating sets of two operadic ideals $I_1$ and $I_2$
is a generating set of $I_1+I_2$, so that the union of generating
relations for the two operads $\Oca_1$ and $\Oca_2$ of $\QMag$ forms a
generating set for the relations of $\Oca_1\InfQMag\Oca_2$. However, the
authors do not know how to compute a generating set of the intersection
of ideals (it is not the intersection of the generating relations), so
that we do not know how to compute generating relations
for~$\Oca_1\SupQMag\Oca_2$.
\medbreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hilbert series and Grassmann formula}
In order to show a Grassmann formula analog for $\LatQMag$, we need the
following lemma.
\medbreak

\begin{Lemma}
    \label{lem:lattice_structure_and_coefficients_of_Hilbert_series}
    Let $\Oca_1$ and $\Oca_2$ be two operads of $\QMag$. For every
    positive integer~$n$, we have
    \begin{equation}
    \label{equ:lattice_structure_and_coefficients_of_the_Hiblert_series}
        \dim{\left(\left(\Oca_1\InfQMag\Oca_2\right)(n)\right)}+
        \dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)(n)\right)}=
        \dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}.
    \end{equation}
\end{Lemma}
\begin{proof}
    Let $I_1, I_2 \in \IMag$ such that $\Oca_1 = \KMag/_{I_1}$ and
    $\Oca_2 = \KMag/_{I_2}$. For every positive integer $n$, we have
    \begin{equation}\begin{split}
        \dim & {\left(\Oca_1\InfQMag\Oca_2(n)\right)}+
            \dim{\left(\Oca_1\SupQMag\Oca_2(n)\right)}\\
        &=\dim{\Big(\KMag(n)/_{\left(I_1+I_2\right)(n)}\Big)}+
            \dim{\Big(\KMag(n)/_{\left(I_1\cap I_2\right)(n)}\Big)}\\
        &=\dim{\left(\KMag(n)\right)}-\dim{\left(I_1(n)+I_2(n)\right)}
            +\dim{\left(\KMag(n)\right)}
            -\dim{\left(I_1(n)\cap I_2(n)\right)} \\
        &=\dim{\left(\KMag(n)\right)}-\dim{\left(I_1(n)\right)}
            + \dim{\left(\KMag(n)\right)}-\dim{\left(I_2(n)\right)}\\
        &=\dim{\Big(\KMag(n)/_{I_1(n)}\Big)}
            +\dim{\Big(\KMag(n)/_{I_2(n)}\Big)}\\
        &=\dim{\left(\Oca_1(n)\right)}+\dim{\left(\Oca_2(n)\right)}.
    \end{split}\end{equation}
    The third equality is due to the Grassmann formula applied to the
    subspaces $I_1(n)$ and $I_2(n)$ of $\KMag(n)$.
\end{proof}
\medbreak

@@

\begin{Theorem}
    \label{thm:Grassmann_formula_for_Hilbert_series_of_QMag}
    Let $\Oca_1$ and $\Oca_2$ be two operads of $\QMag$. We have
    \begin{equation} \label{equ:lattice_structure_and_Hiblert_series}
        \HilbertSeries_{\Oca_1\InfQMag\Oca_2}(t)
        +\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)
        =\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t).
    \end{equation}
\end{Theorem}
\begin{proof}
    We have
    \begin{equation}\begin{split}
        \HilbertSeries_{\Oca_1\InfQMag\Oca_2}(t)
        +\HilbertSeries_{\Oca_1\SupQMag\Oca_2}(t)&
        =\sum_{n \geq 1}\dim{\left(\left(\Oca_1\InfQMag\Oca_2\right)(n)
            \right)}t^n
            +\sum_{n \geq 1}\dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)
            (n)\right)}t^n\\
        &=\sum_{n \geq 1}\Big(\dim{\left(\Oca_1\InfQMag\Oca_2(n)\right)}
            +\dim{\left(\left(\Oca_1\SupQMag\Oca_2\right)(n)
        \right)}\Big)t^n\\
        &=\sum_{n \geq 1}\Big(\dim{\left(\Oca_1(n)\right)}
            +\dim{\left(\Oca_2(n)\right)}\Big)t^n\\
        &=\sum_{n \geq 1}\dim{\left(\Oca_1(n)\right)}t^n+\sum_{n \geq 1}
            \dim{\left(\Oca_2(n)\right)}t^n\\
        &=\HilbertSeries_{\Oca_1}(t)+\HilbertSeries_{\Oca_2}(t),
    \end{split}\end{equation}
    where the third equality is due to
    Lemma~\ref{lem:lattice_structure_and_coefficients_of_Hilbert_series}.
\end{proof}
\medbreak

\Todo{S: ce thm est une "série génératriciation" du lemme précédent. Je
serais d'avis de supprimer ce lemme et de montrer directement le thm.
Avec l'espace gagné, je propose de donner pour cette partie un exemple:
deux quotients --- linéaires --- de Mag dont on donne les séries
de Hilbert (quitte à ne pas les démontrer, mais pour illustrer le thm).}

### 2018-09-07 Operads_rewrite.tex
Passe partie 2

    \item Go to Step~\ref{item:loop_start_buchberger}.
\end{enumerate}
The set of rewrite rules $\Rew'$ outputted by this semi-algorithm is a
\Def{completion} of $\Rew$. By Lemma~\ref{lem:degree_confluence},
$\RewContext'$ is confluent. Notice that, for certain inputs $\Rew$,
this semi-algorithm never stops. Notice also that the computed
completion depend on the total order $\leq$ on the binary trees of a
same arity, the choices at Steps~\ref{item:choice_branching_tree}
and~\ref{item:choice_branching_pair} as well as the computed normal
forms at Step~\ref{item:computed_normal_forms}.
\medbreak

>>>>

    \item Go to Step~\ref{item:loop_start_buchberger}.
\end{enumerate}
The set of rewrite rules $\Rew'$ outputted by this semi-algorithm is a
\Def{completion} of $\Rew$. By Lemma~\ref{lem:degree_confluence},
$\RewContext'$ is confluent. Notice that, for certain inputs $\Rew$,
this semi-algorithm never stops. Notice also that the computed
completion depends on the total order $\leq$ on the binary trees of a
same arity, the choices at Steps~\ref{item:choice_branching_tree}
and~\ref{item:choice_branching_pair} as well as the computed normal
forms at Step~\ref{item:computed_normal_forms}.
\medbreak
